### 2012-11-09 counterexample to bratman on shared intention/a counterexample to bratman on shared intention.tex
before removing old stuff

\section{Shared Intention}
Why, if at all, is a notion of shared intention needed? 
This question is standardly answered by appeal to contrast cases \citep[compare][p.\ 150]{Bratman:2009lv}.
Thus \citet{gilbert_walking_1990} contrasts our intentionally walking together with two people who happen to be walking side by side. 
And \citet{Searle:1990em} contrasts park visitors who  simultaneously run to a central shelter in performing a dance with park visitors who likewise run to the central shelter but only because of an impending storm. 
These and other contrast cases invite the question, 
How does our intentionally acting together differ from our merely acting in parallel? 
The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who are merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be a matter only of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
Many philosophers agree that a notion of shared intention is useful for understanding acting together. 
Compare \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  See also  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 117]{rakoczy_pretend_2006} and 
	\citet{Tollefsen:2005vh}.
	}

@@

`3. 1 and 2 are common knowledge between us' \citep[][p.\ View 4]{Bratman:1993je}
\end{quote}
%
Care is needed in specifying the contents of the intentions concerning our J-ing in these clauses. 
As mentioned above, an appeal to shared intention is supposed to  characterise systematically a difference between two agents who intentionally J together (e.g.\ walk  together) and two agents who also  J together but do not do so intentionally (e.g.\ they happen to be walking side by side). 
So we must avoid tacitly appealing to this distinction by  restricting possible values of J to those which involve our intentionally doing something together. 
Rather the above  conditions, (1)--(3), must be sufficient for shared intention even for some values of J which are `neutral with respect to shared intentionality'.%
\footnote{
 \citet[p.\ 147]{Bratman:1999fr}.
 This refines Bratman's earlier view that some admissable values of J are cooperatively neutral 
 	where an  act-type is \emph{cooperatively neutral} just if `joint performance of an act of that type may be cooperative, but it need not be' \citep[p.\ 330]{Bratman:1992mi}. 
}

A consequence is that, in the right situations, one of us can rationally intend that we J, and can intend this unilaterally, that is without depending on anyone else intending that we J. 
Suppose you know that I am going to Chicago via a certain route at a particular time, 
and that I will do this regardless of what you do.
Suppose also that you can rationally intend that you go to Chicago in the same manner.
Then you can rationally intend that we go to Chicago together, 
	and you can intend this irrespective of whether I have any corresponding intention---providing, of course, that in so intending you are conceiving of our going to Chicago together in a way that is neutral with respect to shared intentionality.
What follows depends on the premise that this is indeed possible.%
\footnote{ 
\citet{Bratman:1999fr}  defends this claim at length. 
Note also that this claim must be true if Bratman's account of shared intention is to provide an informative way of distinguishing between the contrast cases mentioned at the start.
}

In this paper we give a counterexample to Bratman's  claim that the above conditions, (1)--(3), are collectively sufficient conditions for shared intention. 
We shall also suggest a revision which would enable the counterexample to be avoided.
Apart from improving our understanding of what shared intention is, 
this will also bear on the kinds of planning that are involved in acting together.

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim} is that for any J, these conditions are sufficient for you and I to intend that we J.
One of Bratman's aims is to show that it is possible to give an account of shared intention using concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.

\section{Unshared Intentions}
Before we can introduce the counterexample we need to introduce what we shall call `unshared intentions'.
We have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

@@

3. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.

Let us first introduce the activity we shall focus on.
Ayesha and Benji  are playing a simple video game which involves moving a cross around a two-dimensional space littered with barriers.
Ayesha can only accelerate the cross backwards or forwards,
while Benji can only accelerate it left or right. 
The cross moves around and interacts with the barriers in ways both players can predict.
The players are given tasks independently. 
These tasks always involve making the cross hit a target within two minutes of starting. 
A player succeeds when the cross hits her target, regardless of what happens to the cross afterwards.  
(It may go on to hit another target.)
In this case, 
	Ayesha's task is to make the cross hit the red square
	while
	Benji's task is make the cross hit the blue circle. 
In general it is possible that either or both will succeed, or that they will both fail.
Each movement carries a small cost to the player who moves, so that Ayesha and Benji each attempt to minimize how much he or she moves the cross consistently with completing his or her task.
Ayesha and Benji are each neutral on whether the other succeeds or fails.
They are not opponents and do not seek to undermine each other's efforts, but each is entirely concerned  with his or her own task.
All of this is common knowledge for Ayesha and Benji.
They both know who has which task, what constraints they face and what their motives are.

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence actions, <a$_1$, a$_2$, ...\ a$_n$>, then Benji will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, we could say, truthfully, that Ayesha and Benji made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Benji, make the cross hit the red square.

Unshared intentions require a kind of symmetry.
Let us suppose that the above sequences of actions,
	Ayesha's <a$_1$, a$_2$, ...\ a$_n$>  and 
	Benji's <b$_1$, b$_2$, ...\ b$_n$>,
will also result in the cross hitting the blue circle. 
(Since the cross has momentum, we can suppose that it will hit both the red square and the blue circle at some time after these actions are performed.)
Then by the reasoning just offered, Benji could intend that they, Ayesha and Benji make the cross hit the blue circle.
So Ayesha and Benji could meet the first condition, (1), for having an unshared intention.

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To make sense of this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way we could <J$_1$, J$_2$> that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
there would be a failure to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Benji out of the way and seizing his controls. 
But in the case we have been describing there is no such failure to mesh.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Benji, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Benji likewise for making the cross hit the blue circle.

@@

\section{Pure unshared intentions and imaginary agents [*cut?]}
An unshared intention is \emph{pure} if having that unshared intention does not involve having any shared intention. 
It may initially appear obvious that all unshared intentions are pure. 
This is not obvious, however.
Since Bratman provides only sufficient conditions for shared intention, his account doesn't tell us that the unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might also be collectively sufficient conditions for shared intention. 
And while we might be tempted to assume that for two agents to intentionally J together they must at least each have intentions concerning J, 
this assumption might reasonably be rejected by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
So the purity of an unshared intention cannot be assumed without argument.

For reasons to be explained later, we need to show that  Ayesha and Benji's unshared intention that they <J$_1$, J$_2$>  is pure.
How could we do this? 
Ayesha sees Benji's actions as constraints on her own, or else as opportunities.
She exploits Benji's intentions for her own ends.
Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting.
The sort of shared agency that an account of shared intention is supposed to capture must involve more than this sort of reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities. 
Intuitively shared agency must somehow involve greater unity.
But how can this intuition support an argument?

We started this paper by explaining the need for a notion of shared intention by appeal to contrast cases (following Bratman). 
It is contrast cases that are supposed give us a pre-theoretical handle on shared intention.
So to show that Ayesha and Benji's unshared intention is pure, we need to construct a contrasting case.

***Lily and Isabel, 
	like many people, 
 	sometimes attribute intentions and other states to imaginary agents, and perform actions on their behalf. 
In some cases this enables them to further their own real-world objectives (as in `Teddy wants to go to the park now').	
Some of these imaginary agents are toys. 
But some are imaginary aggregate agents. 
Sometimes, that is, Lily and Isabel imagine that there is an agent distinct from either of them and such that all its parts are parts of them.
They attribute intentions and other states to this agent, and act on its behalf.

An account of shared intention should enable us to  distinguish systematically between two types of case in which we J together, one where we intentionally J together and the other where  our J-ing together involves  merely parallel actions.
As noted, Gilbert's example of walking together shows that merely parallel actions can be mutually responsive, as when two strangers walking side by side avoid collision thanks to meshing subplans.

@@

In the situation just described,
Ayesha and Benji are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Yasmin and Zak, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Benji's except for one detail.
Just by chance they have been assigned identical tasks: Yasmin's task is to make the cross hit the red square and Zak's task is the same.
So where Ayesha and Benji have an unshared intention that they <J$_1$, J$_2$>,
Yasmin and Zak meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But these intentions, the unshared intention and the Bratman intention (as we might label the structure of intention and knowledge while leaving open whether it constitutes a shared intention), result in them performing same actions in the same way.
That is, Yasmin reasons about Zak much as Ayesha reasons about Benji and Yasmin and does what Ayesha does, and likewise for Zak and Benji.

We shall argue that Yasmin and Zak do not have a shared intention that they J$_1$ despite meeting meet Bratman's conditions (1)--(3).
This is probably not yet obvious, however.
Let us first attempt to provide some intuitive support for this claim.
Return to Ayesha and Benji for a moment.
Ayesha sees Benji's actions as constraints to work around and opportunities to exploit.
She exploits Benji's intentions for her own ends.
Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting.
The sort of shared agency that an account of shared intention is supposed to capture must involve more than this sort of reciprocal exploitation, where each agent merely exploits the other's intentions. 
But Yasmin and Zak are engaged in just the same sort of reciprocal exploitation as Ayesha and Benji.
The only difference is that, quite by chance, Yasmin's task and Zak's task are the same.
So, intuitively, Yasmin and Zak, like Ayesha and Benji, belong in the same category as two people who happen to be walking side by side and not in the category exemplified by two people intentionally walking together.

Assuming for a moment that this is right,
what might explain the difference between Yasmin and Zak on the one hand and cases like Gilbert's two people intentionally walking together on the other hand?
To answer this question in the spirit of Bratman's planning-theoretic approach, we need to step back and think about planning generally.

>>>>

\section{Shared Intention}
Why, if at all, is a notion of shared intention needed? 
This question is standardly answered by appeal to contrast cases \citep[compare][p.\ 150]{Bratman:2009lv}.
Thus \citet{gilbert_walking_1990} contrasts our intentionally walking together with two people who happen to be walking side by side. 
And \citet{Searle:1990em} contrasts park visitors who  simultaneously run to a central shelter in performing a dance with park visitors who likewise run to the central shelter but only because of an impending storm.
%And Bratman (\citeyear{Bratman:1992mi}, p.\ 333; \citeyear{Bratman:1993je}, p.\ 103--4) contrasts two people who cooperatively plan to go to New York  together with two people who each have an intention that they go to New York together by way of coercing the other into travelling with her.
These and other contrast cases invite the question, 
How do cases involving shared agency differ from cases involving parallel agency only?

The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who are merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be  only a matter of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
Many philosophers agree that a notion of shared intention is useful for understanding acting together. 
Compare \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  See also  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 117]{rakoczy_pretend_2006} and 
	\citet{Tollefsen:2005vh}.
	}

@@

`3. 1 and 2 are common knowledge between us' \citep[][p.\ View 4]{Bratman:1993je}
\end{quote}
%
In this paper we give a counterexample to Bratman's  claim that the above conditions, (1)--(3), are collectively sufficient conditions for shared intention. 
We shall also suggest a revision to avoid the counterexample.
%Apart from improving our understanding of what shared intention is, this will also bear on the kinds of planning that are involved in acting together.

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim} is that for any J, these conditions are sufficient for you and I to intend that we J.
One of Bratman's aims is to show that an account of shared intention can be \emph{conceptually conservative}:
he aims, that is, to show that it is possible to give an account of shared intention using concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.

How could we show that our meeting Bratman's conditions, (1)--(3), is not in fact sufficient for us to have a shared intention? 
We seek a case where the conditions are met although we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving parallel agency only (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some relevant J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike, 
	that in each case the structure of intention and knowledge played an appropriate role in guiding the agents' actions,
	and that in each case the agents thereby successfully J.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.

Several preliminaries are necessary for the construction of our counterexample. 
These preliminaries might easily give the impression that our counterexample depends on an artificial settings. 
However, having introduced the primary counterexample in an artificial setting, we will  go on to show that counterexamples can also be constructed for mundane activities including walking together.

%%
%%two agents who intentionally J together (e.g.\ walk  together) and two agents who also  J together but do not do so intentionally (e.g.\ they happen to be walking side by side). 
%%
%This has two consequences.
%First, it should be impossible to construct a pair cases, A and B,
%meeting these criteria:
%	(i) in each case, two agents act intentionally;
%	(ii) in the first case, the two agents do not meet conditions (1)--(3) above;
%	(iii) in the second case, the agents do meet conditions (1)--(3) above;
%	(iv) the cases, A and B, are otherwise as similar as possible;
%	and 
%	(v) neither A nor B exemplifies the sort of shared agency gestured at by appeal to the contrast cases we started with.
%Second, it should also be impossible to construct a pair cases, B and C,
%meeting these criteria:
%	(i$^\prime$) in each case, two agents act intentionally;
%	(ii$^\prime$) in each case, the agents do meet conditions (1)--(3) above;
%	and 
%	(iii$^\prime$) C but not B exemplifies the sort of shared agency gestured at by appeal to the contrast cases we started with.
%
%
%
%
%Let's stipulate that two cases \emph{differ with respect to shared agency} when they differ in the way exemplified by the contrast between our intentionally walking together and our merely walking in parallel.
%Suppose, then, that we construct three cases, A, B and C.
%The three cases are as similar as possible, except that the above conditions are met in cases B and C but not in case A.
%Now if Bratman's conditions are sufficient for shared intention, A should differ from B with respect to shared agency, and B should not differ from C with respect to shared agency.
%But suppose that in fact A does not differ from B with respect to shared agency, whereas B does so differ from C.%
%\footnote{
%Strictly speaking only A and B are needed for the counterexample, of course.
%But including C makes it clearer that A and B do not differ with respect to shared agency.
%}
%Then we can conclude that Bratman's conditions are not sufficient for shared intention.
%This is how our counterexample will work.

\section{Neutral with Respect to Shared Intentionality}
Before we can introduce the counterexample 
we need to highlight a feature of Bratman's account 
	which we shall be exploiting.

Consider the contents of the intentions concerning our J-ing in the above clauses, (1)--(3). 
What sort of activity can you intend when you intend that we J?
We cannot restrict possible values of J to activities which involve shared agency.
In imposing any such restriction we would be assuming the very notion that an account of shared intention is supposed to illuminate. 
%
%As we have stressed, 
%	make it possible to 
%	characterise systematically a difference between 
%		cases involving shared agency (such as our walking together)
%		and
%		cases involving parallel agency only (such as two strangers who happen to be walking the same route side-by-side). 
%We must therefore avoid tacitly appealing to this distinction by  restricting possible values of J to those which involve shared agency. 
Rather the above  conditions, (1)--(3), must be sufficient for shared intention even for some values of J which are `neutral with respect to shared intentionality'.%
\footnote{
 \citet[p.\ 147]{Bratman:1999fr}.
 This refines Bratman's earlier view that some admissable values of J are cooperatively neutral 
 	where an  act-type is \emph{cooperatively neutral} just if `joint performance of an act of that type may be cooperative, but it need not be' \citep[p.\ 330]{Bratman:1992mi}. 
}

A consequence is that, in the right situations, one of us can rationally intend that we J, and can intend this unilaterally, that is without depending on anyone else intending that we J. 
Suppose you know that I am going to Chicago via a certain route at a particular time, 
and that I will do this regardless of what you do.
Suppose also that you can rationally intend that you go to Chicago in the same manner,
and that you know that if you act on this intention the upshot will be that we will go to Chicago together (although I may not know that we are going together---perhaps you will conceal your presence from me).
Then you can rationally intend that we go to Chicago together, 
	and you can intend this irrespective of whether I have any corresponding intention---providing, of course, that in so intending you are conceiving of our going to Chicago together in a way that is neutral with respect to shared intentionality.
What follows depends on the premise that this is indeed possible.%
\footnote{ 
\citet{Bratman:1999fr}  defends this claim at length. 
Note also that this claim must be true if Bratman's account of shared intention is to provide an informative and systematic distinction between the contrast cases mentioned at the start.
}

\section{Unshared Intentions}
As a further preliminary we need to introduce a definition.
Let us stipulate that we have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

@@

3. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.
This possible situation is not the promised counterexample, but it does form the basis for it.

Let us first introduce the activity we shall focus on.
Ayesha and Benji  are playing a simple video game which involves moving a cross around a two-dimensional space littered with barriers.
Ayesha can only accelerate the cross backwards or forwards,
while Benji can only accelerate it left or right. 
The cross moves around and interacts with the barriers in ways both players can predict.
The players are given tasks independently. 
These tasks always involve making the cross hit a target within two minutes of starting. 
A player succeeds when the cross hits her target, regardless of what happens to the cross afterwards.  
(It may go on to hit another target.)
In this case, 
	Ayesha's task is to make the cross hit the red square
	while
	Benji's task is make the cross hit the blue circle. 
In general it is possible that either or both will succeed, or that they will both fail.
Each movement carries a small cost to the player who moves, so that Ayesha and Benji each attempt to minimize how much he or she moves the cross consistently with completing his or her task.
At the outset, 
Ayesha and Benji are each neutral on whether the other succeeds or fails.
They are not opponents and do not seek to undermine each other's efforts, but each is entirely concerned  with his or her own task.
All of this is common knowledge for Ayesha and Benji.
They both know who has which task, what constraints they face and what their motives are.

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence actions, <a$_1$, a$_2$, ...\ a$_n$>, then Benji will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, it would be true that Ayesha and Benji made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Benji, make the cross hit the red square.

Unshared intentions require a kind of symmetry.
Let us suppose that the above sequences of actions,
	Ayesha's <a$_1$, a$_2$, ...\ a$_n$>  and 
	Benji's <b$_1$, b$_2$, ...\ b$_n$>,
will also result in the cross hitting the blue circle. 
(Since the cross has momentum, we can suppose that it will hit both the red square and the blue circle at some time after these action sequences have been performed.)
Then by the reasoning just offered, Benji could intend that they, Ayesha and Benji make the cross hit the blue circle.
So Ayesha and Benji could meet the first condition, (1), for having an unshared intention.

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To make apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
there would be a failure to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Benji out of the way and seizing his controls. 
There would also be a failure of mesh if Ayesha were planning to trick Benji into a situation where we would be unable to perform the actions he had been planning.
But in the case we have been describing there are no such failures to mesh.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Benji, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Benji likewise for making the cross hit the blue circle.

@@

%\section{Pure Unshared Intentions}
%We stipulate that an unshared intention is \emph{pure} if having that unshared intention does not involve having any shared intention. 
%It may be tempting to assume that all unshared intentions are pure. 
%This is not obvious, however, and may not even be true.
%Since Bratman provides only sufficient conditions for shared intention, his account doesn't tell us that an unshared intention is not a shared intention.
%For all Bratman says, the conditions defining unshared intention might also be collectively sufficient conditions for shared intention. 
%
%But doesn't shared agency require that there be a single activity, J-ing, about which each the agent involved has an intention? 
%This, too, is not obvious.  It might reasonably be denied by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
%So the purity of an unshared intention cannot be assumed without argument. 
%This is why we do not rely on this assumption in what follows.
%
%%
%How can we show that Ayesha and Benji's unshared intention that they <J$_1$, J$_2$>  is pure?
%Perhaps we can appeal to intuition.
%Ayesha sees Benji's actions as constraints on her own, or else as opportunities.
%She exploits Benji's intentions for her own ends.
%Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
%Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
%and this is the full extent of their cooperation. 
%Perhaps it is clear enough that 
%the sort of shared agency that an account of shared intention is supposed to capture must involve more than this sort of reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.%
%\footnote{
%Note that we are not suggesting that reciprocal exploitation is incompatible with shared agency.  
%The claim under consideration here is rather that shared agency requires more than reciprocal exploitation.
%} 
%If so, we can already claim that Ayesha and Benji have a pure unshared intention.
%
%
%
%
%
%We started this paper by explaining the need for a notion of shared intention by appeal to contrast cases (following Bratman). 
%It is contrast cases that are supposed give us a pre-theoretical handle on shared intention.
%So to show that Ayesha and Benji's unshared intention is pure, we need to construct a contrasting case.
%
%***Lily and Isabel, 
%	like many people, 
% 	sometimes attribute intentions and other states to imaginary agents, and perform actions on their behalf. 
%In some cases this enables them to further their own real-world objectives (as in `Teddy wants to go to the park now').	
%Some of these imaginary agents are toys. 
%But some are imaginary aggregate agents. 
%Sometimes, that is, Lily and Isabel imagine that there is an agent distinct from either of them and such that all its parts are parts of them.
%They attribute intentions and other states to this agent, and act on its behalf.
%
%
%

%
%An account of shared intention should enable us to  distinguish systematically between two types of case in which we J together, one where we intentionally J together and the other where  our J-ing together involves  merely parallel actions.
%As noted, Gilbert's example of walking together shows that merely parallel actions can be mutually responsive, as when two strangers walking side by side avoid collision thanks to meshing subplans.

@@

In the situation just described,
Ayesha and Benji are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Yasmin and Zak, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Benji's except for one detail.
Just by chance they have been assigned identical tasks: Yasmin's task is to make the cross hit the red square and Zak's task is the same.
So where Ayesha and Benji have an unshared intention that they <J$_1$, J$_2$>,
Yasmin and Zak meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Yasmin, in planning and acting, does not rely on the coincidence of their intentions; and nor does Zak.
(Yasmin relies on the fact Zak intends that they J$_1$, of course; but she does not rely on the fact that Zak intends what she intends.)
Furthermore, due to an artefact of the way the game is structured,
the unshared intention and the Bratman intention (as we might label the structure of intention and knowledge while leaving open whether it constitutes a shared intention), result in the two pairs performing same actions in the same way.
That is, Yasmin reasons about Zak much as Ayesha reasons about Benji and Yasmin and does what Ayesha does, and likewise for Zak and Benji.

We claim that Yasmin and Zak have a shared intention that they J$_1$
only if 
Ayesha and Benji have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether or not Ayesha and Benji have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Yasmin and Zak lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ in virtue of meeting Bratman's conditions. 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Yasmin and Zak happen to be assigned the same task, whereas Ayesha and Benji are not.
And neither Yasmin nor Zak makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider on how  
		the case of Yasmin and Zak
	differs from
		 that of Ayesha and Benji,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

To show that the case of Yasmin and Zak do not have a shared intention it remains only for us to show that Ayesha and Benji do not have one. 
Here we must be careful.
First note that,
	 since Bratman provides only sufficient conditions for shared intention, 
	 his account doesn't tell us that an unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might  be sufficient for shared intention.

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally F-s she has an intention concerning her F-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Zak lack a shared intention
	just because (by construction) there is no F such that Ayesha and Zak's each intend that they, Ayesha and Zak, F.

Can we then appeal directly to intuition to show that Ayesha and Zak lack a shared intention?
Ayesha sees Benji's actions as constraints on her own, or else as opportunities.
She exploits Benji's intentions for her own ends.
Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Zak's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Benji are not acting on a shared intention.
But philosophers' intuitions about shared agency may not be entirely, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Yasmin and Zak lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next section we shall further support our claim by contrasting Yasmin and Zak's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Yasmin and Zak's case contrasts with this new case will support the claim that Yasmin and Zak lack shared intention.
This is the aim of the following section.
A first motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

\section{Agent-neutral Plans}

Above we introduced what will turn out to be a counterexample to Bratman's account, the case of Yasmin and Zak. 
But we have yet to show that this case really is a counterexample. 
For all we have said so far, a proponent of Bratman's view might insist that Yasmin and Zak do have a shared intention.
To show that they do not,
we shall contrast Yasmin and Zak's case with a third case that is as similar as possible but does involve shared intention.

%---the following is a mistake (because Yasmin and Zak do take each other's task into account.
%It is unlikely that humans would spontaneously behave as Yasmin and Zak do.%
%\footnote{
%This is nicely illustrated in a series of experiments by Sebanz and colleagues in which subject spontaneously take another's plans into account in planning their own actions, even where doing so is manifestly not required and can impair their performance  \citep{Sebanz:2003kf,Sebanz:2005fk,tsai:2011_groop_effect}.
%}

First we need to introduce the notion of an agent-neutral plan.
We stipulate that a planning process, or a plan, is \emph{agent-neutral} just if it does not involve identifying any particular agents.  
This sort of planning is quite common.
For example, some housemates who have decided to take on an allotment to grow vegetables might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
(This is an idealisation, of course.)
At some point the planning is done  and they divide up the roles.
Of course they may not find a way of dividing up roles that everyone is prepared to go along with---individuals' preferences, abilities and intentions may block the plan's adoption.
But suppose the housemates do divide up the roles in a way that is acceptable to everyone, 
	and that each implements her part in the plan.
Then each conceives of her own and the others' actions as part of single plan directed to achieving a single outcome.
